---
title: "Assigning WCR P450s to CYP families"
output: html_notebook
---

Having clustered WCR P450s into groups based on %identity, and then assigned groups to CYP families, now we want to map the family assignments to individual P450s. This can be done easily with the database-like functionality found in dplyr.

# Load libraries

```{r}
library(dplyr)
library(stringr)
```

# Load data

```{r}
wcr.p450s <- read.table("WCRCYPGroups.tsv",
                        header = T,
                        stringsAsFactors = F)

wcr.p450.families <- read.table("WCRCYPGroupsFamilies.tsv",
                                header = T,
                                stringsAsFactors = F)
```

Use a `left_join` to map familes to individual genes.

```{r}
wcr.p450.assigned <- left_join(wcr.p450s, 
                               wcr.p450.families, 
                               by = "group")[,c(1,6)]

```

Out of interest, what's the distribution of genes among families?

```{r}
tab <- table(wcr.p450.assigned$family)
tab
```

```{r}
barplot(tab, 
        las = 2,
        cex.names = 0.75,
        col = "steelblue2")

```

Write out a table with the gene - family associations. Note that PRALINE likes to change the `.` at the end of transcript names to `_`. Change them back so we are consistent with Apollo, etc.

```{r}
wcr.p450.assigned$gene <- str_replace(str_replace_all(wcr.p450.assigned$gene, 
                                                      "_", 
                                                      "\\."), 
                                      "XM.", 
                                      "XM_")

```

```{r}
write.table(wcr.p450.assigned,
            file = "WCRCYPFamilies.tsv",
            quote = F,
            row.names = F,
            sep = '\t')
```

